Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-08-27 manuscript/manuscript.Rmd
Fixes to plots.

# Base font size.
base_size <- 10

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(0.8)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")

@@

In this section, we will first introduce location and scale invariant versions of the Box-Cox and Yeo-Johnson transformations.
Subsequently, we define weighted location and scale invariant transformations and weighting methods that allow for defining robust transformations.
For the purpose of simulation we then define the quantile function for asymmetric generalised normal distributions.
Finally, we define the overall framework for the empirical central normality test.

@@

```{r marginal-effect-plot, echo=FALSE, fig.cap=cap, fig.height=12.0, warning=FALSE}
cap <- paste0(
  "Estimated marginal effect of learners, normalisation and transformation methods on ranked model performance scores in 22800 machine learning experiments on 285 datasets. ",
  "The top-left panel shows the marginal effect of learners, i.e. random forests and generalised linear models (GLM). ",
  "Random forests outperform GLM models for all task difficulties. ",
  "The top-right panel shows the marginal effect of feature normalisation methods, i.e. no normalisation and z-standardisation. ",
  "z-standardisation is generally beneficial, but the estimated effect is neglible. ",
  "The bottom panel shows the marginal effects of different transformation methods, split by learner and normalisation method. ",
  "There is no consistent behaviour, and estimated effects are neglible. ",
  "Note that the ranges of the $x$-axes of the three main panels differ. ",
  "ECTN: empirical central normality test."
)

>>>>

# Base font size.
base_size <- 9

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")
plot_theme$legend.title

@@

In this section, we will first introduce location and scale invariant versions of the Box-Cox and Yeo-Johnson transformations.
Subsequently, we define weighted location and scale invariant transformations and weighting methods that allow for defining robust transformations.
We then define the quantile function for asymmetric generalised normal distributions to enable random sampling.
Finally, we define the overall framework for the empirical central normality test.

@@

```{r marginal-effect-plot, echo=FALSE, fig.cap=cap, fig.height=7.5, warning=FALSE}
cap <- paste0(
  "Estimated marginal effect of learners, normalisation and transformation methods on ranked model performance scores in 22800 machine learning experiments on 285 datasets. ",
  "The top-left panel shows the marginal effect of learners, i.e. random forests and generalised linear models (GLM). ",
  "Random forests outperform GLM models for all task difficulties. ",
  "The top-right panel shows the marginal effect of feature normalisation methods, i.e. no normalisation and z-standardisation. ",
  "z-standardisation is generally beneficial, but the estimated effect is neglible. ",
  "The bottom panel shows the marginal effects of different transformation methods, split by learner and normalisation method. ",
  "There is no consistent behaviour, and estimated effects are neglible. ",
  "Note that the ranges of the $x$-axes of the three main panels differ. ",
  "ECTN: empirical central normality test."
)
